Autonomous Quadrotor Landing on a Moving Platform

### 2016-02-27 docs/interim_report/interim_report.tex
Add interim report

% GRAPHICS
\usepackage{float}
\usepackage{graphicx}

@@

% DOCUMENT PADDING AND MARGINS
\usepackage{titlesec}
\usepackage[margin=1.2in]{geometry}
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{2ex}{0ex}
\titlespacing*{\subsection}{0pt}{1ex}{-2ex}
\titlespacing*{\subsubsection}{0pt}{2ex}{-2ex}

@@

\section*{Introduction}
Our goal is to autonomously land a quadrotor onto a moving platform. In this 
interim-report we will discuss our efforts so far, and any preliminary results 
we may have. So far we have spent a considerable amount of effort getting 
different components of the project working. In this report we will be 
discussing progress in both hardware and software aspects of the project, 
specifically:

\begin{itemize}
	\vspace{-0.4cm}
	\setlength{\itemsep}{0pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}

	\item{Quadrotor Setup and Onboard Computer}
	\item{Camera}
\end{itemize}

\section*{Hardware}
For the hardware, we have chosen to reuse equipment that is readily available 
to us in the Wave Lab. For the quadrotor we are using

@@

\section*{Software}
\subsection*{Pixhawk Firmware}

\subsection*{Simulator}

\subsection*{AprilTag}

>>>>

% GRAPHICS
\usepackage{float}
\usepackage{graphicx}
\usepackage{subcaption}

@@

% DOCUMENT PADDING AND MARGINS
\usepackage{titlesec}
\usepackage[margin=1.5in]{geometry}
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{2ex}{0ex}
\titlespacing*{\subsection}{0pt}{1ex}{-2ex}
\titlespacing*{\subsubsection}{0pt}{2ex}{-2ex}

@@

\section*{Introduction}
Our goal is to autonomously land a quadrotor onto a moving platform, the main 
significance of this work is to disgard GPS and perform autonomous precision 
landing using low cost sensors, such as sonar and vision.

In this interim-report we will discuss our progress, and any preliminary 
results we may have. So far we have spent a considerable amount of effort 
getting different components of the project working. In this report we will be 
discussing changes, progress in both hardware and software aspects of the 
project and remaining project schedule.

\section*{Changes in Direction or Project Scope}

Due to time constraints, we will be forgoing our idea of using gimbal cameras 
for this project. We initially had hoped we would be using the gimbal camera 
to locate the landing target from afar and approach the target.

Since we are omitting gimbal cameras, we will be assuming that the 
quadrotor will be directly above the moving landing target as its intial 
conditions, and that is where our autonomous system will be to start its 
autonoums precision landing.

\section*{Project Progress}
\subsection*{Hardware}
\subsubsection*{Quadrotor Setup}
For the hardware, we have chosen to reuse equipment that is readily available 
to us in the Wave Lab. For the quadrotor we have been using the DJI F450 
quadrotor frame, Emax 2213-935KV motors with complimentary 1045R propellers, 
Thunder Power lipo 11.1V 4200mah battery, DJI E310 420S 20A electronic speed 
controller and Pixhawk v2.4 as our flight controller. At current our quadrotor 
flies reasonably well with some \textit{minor} setbacks, mainly due to the 
instability of the firmware, and lack of good documentation for the firmware 
and software packages. Our problems thus far with the quadcopter are mostly 
software based.

@@

\subsubsection*{Onboard Autonomous Control System}
In terms of onboard autonoumos control, we have decided to use the Odriod 
XU4 due to its size and processing power available, and a Logitech C270 HD 
webcam as our vision sensor. One problem we may face very soon is the narrow 
field of view and relatively low frame rate (25Hz) the logitech webcam has. We 
will be keeping our options open, and plan on replacing the logitech webcam 
with a Ximia xiQ USB3 camera with a wide angle lens in the near 
future.

\subsection*{Software}
\subsubsection*{Pixhawk Firmware}
As mentioned in the hardware section, we have had numerous issues with 
regards to using the software suite for the Pixhawk Flight Controller, 
as well as the PX4 firmware itself. There are many instances where we could not 
explain the instability of the quadrotor during flight, many of which lead to 
costly crashes, but we believe through these experiences we have developed a 
procedure to lower the risk for such instances from happening often.

\subsubsection*{Odriod to Pixhawk Communication}
For our autonomous system to control the quadrotor directly, the Odriod has to 
be able to communicate with the Pixhawk, this is where \verb|mavros| (ROS 
package) comes into play. Mavlink is a popular UAV communication protocol 
between UAV and ground control softwares, \verb|mavros| creates a mavlink ROS 
node to enable developers to monitor and issue mavlink commands with ease. We 
have successfully used mavros to arm and disarm Pixhawk (tested), in the near 
future we should be able to send velocity/attitude commands to control the 
quadrotor.

\subsubsection*{Simulator}
Initially we have explored the possibility of using the combination of PX4's 
Software in the Loop Simulation (SITL) and Gazebo 6 as our simulation 
environment for our project, however we found the combination of install 
instructions changing at a fast pace, and the documentation not up to date to 
be a major concern for us. We have therefore decided to fallback on developing 
the estimation and control loop in Matlab.

\subsubsection*{AprilTag}
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\textwidth]{images/apriltags_1.png}
		\caption{2 Apriltags Detected}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\textwidth]{images/apriltags_3.png}
		\caption{1 Apriltag Detected }
	\end{subfigure}
	\caption{Apriltag Inception - To mitigate the FOV problem}
	\label{fig:apriltag}
\end{figure}

On the landing target from we have successfully calibrated the logitech webcam 
and used the Apriltag library to obtain a pose estimate, and have manually 
verified the estimates are accurate, for distance the error is $\pm 1$cm. We 
have also successfully implemented the ability to identify two different 
apriltags of different sizes (see Fig~\ref{fig:apriltag}), pose estimates from 
both apriltags are equal.

Next is to workout how to transform the measurements from the pose estimates of 
the apriltags in relation to the quadrotor's body frame.

\section*{Schedule}

\begin{itemize}
	\vspace{-0.2cm}
	\setlength{\itemsep}{5pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}

	\item{\textbf{6th March}: Implement and show in simulation that we can land 
	a quadrotor successfully on to a moving platform}
	\item{\textbf{13th March}: Perform Autonomous Flying Outdoors and Implement 
	Control code for the Huskey}
	\item{\textbf{21st March}: Perform Autonomous Flying Indoors}
	\item{\textbf{28th March}: Attempt to Autonomous Land the Quadrotor Indoors}
\end{itemize}

### 2016-02-27 docs/proposal/proposal.tex
Add interim report

\documentclass{article}

@@

% DOCUMENT PADDING AND MARGINS
\usepackage{titlesec}
\usepackage[margin=1.5in]{geometry}
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{2ex}{0ex}
\titlespacing*{\subsection}{0pt}{2ex}{-2ex}
\titlespacing*{\subsubsection}{0pt}{2ex}{-2ex}

@@

% TITLE
\title{Autonomous Quadrotor Landing on a Moving Platform}
\author{Stan Brown \& Chris Choi}
\maketitle

\section*{Introduction}
Landing a quadrotor on a moving platform has been explored by a number of researchers \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}, and there exists a wide range of approaches to the problem. However, to the best of our knowledge, we are not aware of any solution that demonstrates an algorithm that is capable of landing a quadrotor on a moving platform outdoors. It is our goal to replicate one of the successful solutions with the aim of extending the solution to land outdoors.

\subsection*{Applications}
Possible applications for this work include autonomous landing on a boat in high wind conditions, landing on a charging platform, landing in high wind conditions.

\section*{Related Work} 
The problem of autonomous landing on a moving platform seems to be divided into three separate parts in literature. First the quadrotor must plan to rendezvous with its target, next it must detect or sense its target and finally apply a set of controllers to approach the platform, match speed and heading and finally land when safe to do so.

In the majority of the literature reviewed, rendezvous planning was neglected and it was assumed that quadrotor has a clear view of its landing location.

From the literature we reviewed planning is the least concern, perception and control seems to be the main factor to sucess. For perception existing solutions could be as simple as using basic color detection techniques to identify the landing target\cite{Kim2014}, to sophisticated techniques such as \cite{Herisse2012} where they used the optical flow in images captured onboard the quadrotor to obtain necessary relative information for control.

@@

\begin{itemize}
	\vspace{-0.2cm}
	\setlength{\itemsep}{5pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}

@@

	\vspace{-0.2cm}
\end{itemize}

\section*{Milestones}
\begin{enumerate}
	\item{Perform tracking and follow in simulation}
	\item{Perform automated landing in simulation}
	\item{Perform the above successfully in real life}
\end{enumerate}

\section*{Possible Expansion}

Trajectory Planning for high wind or fast moving platform.

\bibliography{proposal}{}
\bibliographystyle{plain}

>>>>

\documentclass{article}[12pt]

@@

% DOCUMENT PADDING AND MARGINS
\usepackage{titlesec}
\usepackage[margin=1.2in]{geometry}
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{2ex}{0ex}
\titlespacing*{\subsection}{0pt}{1ex}{-2ex}
\titlespacing*{\subsubsection}{0pt}{2ex}{-2ex}

%COMMENTING
\usepackage{comment}

@@

% TITLE
\title{Autonomous Quadrotor Landing on a Moving Platform}
\author{Stan Brown \& Chris Choi}
\date{}
\maketitle

\section*{Project Outline}
Landing a quadrotor on a moving platform has been explored by a number of researchers \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}, and there exists a wide range of approaches to the problem. However, to the best of our knowledge, we are not aware of any solution that demonstrates an algorithm that is capable of landing a quadrotor on a moving platform outdoors. It is our goal to replicate one of the successful solutions with the aim of extending the solution to land outdoors. Possible applications for this work include autonomous landing on a boat in high wind conditions, landing on a charging platform.

The problem of autonomous landing on a moving platform seems to be divided into three separate parts in literature. First the quadrotor must plan to rendezvous with its target, next it must detect or sense its target and finally apply a set of controllers to approach the platform, match speed and heading and finally land when safe to do so.

\subsubsection*{Planning}
In the majority of the literature reviewed, rendezvous planning was neglected and it was assumed that quadrotor has a clear view of its landing target. Most authors tend to focus on the detection and estimation of the quadrotor's pose relative to the target and maintaining an accurate estimation throughout the landing procedure which is mostly handled by a series of control loops.

\subsubsection*{Perception and State Estimation}
For perception existing solutions use a variety of simple to complex techniques. In  \cite{Kim2014} a basic color threshold technique was to identify the landing target, while \cite{Herisse2012} used optical flow in images captured on board the quadrotor to obtain necessary relative information for control.

\subsubsection*{Control}
A comparison between a PID and Linear Quadratic Control (LQC) was explored in \cite{Friis2009}. However the authors admit, even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC. In \cite{Herisse2012} a PID controller was developed to land on a oscillating platform in the vertical direction with no lateral movement. While interesting, the solution took over 1 minute to transition from hovering over the landing pad to landing. Additionally the experiments did not seem to account for pitch or roll of the platform.

@@

In reviewing the prior work, a reoccurring problem lies in the difficulty in maintaining an accurate pose estimation between the quadrotor and the landing pad throughout the entire manoeuvre. As the quadrotor approaches the landing pad, visible targets used to guide the quadrotor becomes difficult to locate, causing camera based navigation techniques to fail. Furthermore, in certain conditions the tilt angle of the quadrotor could cause difficulty in maintaining a visual on the landing pad for a downward facing or fixed camera.

To address both of these issues, we propose a novel solution utilizing two cameras and two gimbals. In the proposed set up the quadrotor will have a gimballed camera and so will the moving landing platform. Both of the cameras will have an AprilTag attached allow cameras to track each other and provide two estimations of the quadrotor's current pose relative to the landing platform.

We will replicate the experiment performed by \cite{Ling2014}, where we assume the quadrotor already has a visual of the landing platform. We aim to implement a series of controllers for the approach and landing of the quadrotor to the moving landing platform.

\section*{Hardware and Software Status}

For this project we will be using a DJI F450 Flamewheel quadrotor using the Pixhawk flight controller \cite{pixhawk} running the PX4 firmware \cite{px4}. The gimbal design and camera specifications have yet to be decided, for the prototyping and testing phase we will be using fixed USB cameras. For the AprilTag detection and pose estimation we will use the AprilTag Library implemented by \cite{apriltags}. OpenCV will be used for image analysis tasks and the controllers will be implemented using ROS.

\section*{Milestones and Goals for the Semester}
Over the term we have set a series of goals and deadlines in order to evaluate progress throughout the term. Later on additional goals will be added as the requirements change depending on test results.
\begin{enumerate}
	\item{Evaluate AprilTag detection algorithms and libraries - Jan 15}
	\item{Set the simulation environment in Gazebo - Jan 15} 
	\item{Perform automated landing in simulation - Feb 1}
	\item{Acquire gimbals and cameras and test the tracking code - Feb 7}
	\item{Attempt landing indoors and duplicate the work of \cite{Ling2014} - Feb 19}
	\item{Add the gimbals to the quadrotor and landing pad  - Feb 27}
	\item{Implement the proposed methods outlined above - April 15}
	\item{Attempt to land in outdoor conditions 	- April 20}

\end{enumerate}

\begin{comment}
CHRIS IS A LITTLE BITCH
\begin{itemize}
	\vspace{-0.2cm}
	\setlength{\itemsep}{5pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}

@@

	\vspace{-0.2cm}
\end{itemize}
\end{comment}

\newpage

\bibliography{proposal}{}
\bibliographystyle{ieeetr}
